Tail Indices and Scale Parameters in Financial Time Series

### 2017-02-22 papers/FX/draft.tex
Corrected the condition on K.

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation*}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x < 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation*}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and
\begin{equation}
  \label{eq:xxie1.1}
  0 < K <
  {\alpha \over \alpha + 1}
  (e^r - 1)^\xi
  \exp\left(
    - r \xi
    + {1 \over \alpha}
  \right)
\end{equation}
Equation
\eqref{eq:xxie0} can be re-arranged as
\[
u(v) + b u(\delta v))
=
\E u(C) + b \E [u(C); C < \delta v]
\]
The right-hand-side of the above equation is a functional of the
distribution function of $X$ via eq.\eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v]
\]
\begin{theorem}
  Let
  \[
  G(\alpha, \beta, K, K') =
  \max_{0 < \phi \leq 1} \mathcal U F(\alpha, \beta, K, K', \phi)
  \]
  $G(\alpha, \beta, K, K')$ is monotonically increasing with
  $\alpha$.
\end{theorem}

@@

  \item When $C < \delta v$ implies $X < -q$ for some $q \geq 0$, we have

@@

    Define distribution function $H(x): (0, \infty) \to (0, 1)$ by its

@@

    That is, $(x + K) \ln(1 + x/K)$ defined on $(0, \infty)$ is a convex

@@

    This simplies to

@@

      \hat\phi < {
        g - 1
        (1 - e^{-r}) g - 1

@@

@@

          (K + q)^{\alpha + 1} + b K^{\alpha + 1}
        \right] \alpha e^{1/\alpha}

@@

        (\alpha + 1) K (K + q) 

@@

          (K + q)^{\alpha} + b K^{\alpha}

@@

@@

    Assumption \eqref{eq:xxie1.1} ensures $g > e^r/(e^r - 1)$. Hence the

@@

  \item When $C < \delta v$ implies $X < q$ for some $q > 0$, we have
    \begin{eqnarray*}
      && \mathcal U(F)(\alpha, \beta, K, K', \hat\phi) \\
      &=& \alpha p K^\alpha (1 + b) \int_{-\infty}^0
      [(1 - \hat\phi) e^r + \hat\phi e^x]^{-\xi}
      (K - x)^{-\alpha-1} dx \\
      &&
      + (1 - p) \beta K'^\beta \left[
        (1 + b) \int_0^q + \int_q^\infty
      \right]
      [(1 - \hat\phi) e^r + \hat\phi e^x]^{-\xi} (K' + x)^{-\beta-1} dx    
    \end{eqnarray*}
  \end{enumerate}
  So the same calculation as in the previous case carries through
  with $q = 0$. The same conclusion of
  \[
  \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) > 0
  \]
  stands.
\end{proof}

>>>>

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation*}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x < 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation*}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\[
u(v) + b u(\delta v))
=
\E u(C) + b \E [u(C); C < \delta v]
\]
The right-hand-side of the above equation is a functional of the
distribution function of $X$ via eq.\eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v]
\]
\begin{theorem}
  Let
  \[
  G(\alpha, \beta, K, K') =
  \max_{0 < \phi \leq 1} \mathcal U F(\alpha, \beta, K, K', \phi)
  \]
  Let the disappointment threshold $C < \delta v$ be equivalent to $X < -q$. Assume
  \begin{equation}
    \label{eq:xxie1.1}
    r > -\ln \left\{
      1 - \left[
          {\alpha + 1 \over \alpha}
          {
            \left[
              b K^{\alpha + 1} + (K + q)^{\alpha + 1}
            \right]
            \over
            \left[
              b K^{\alpha+1} \left(1 + {q \over K} \right) + (K + q)^{\alpha + 1}
            \right]
          }
          {
            1 \over K e^{1/\alpha}
          }
      \right]^{1/\xi}
    \right\}
  \end{equation}
  Then $G(\alpha, \beta, K, K')$ is monotonically increasing with $\alpha$.
\end{theorem}

@@

  \item When $q \geq 0$, we have

@@

    Define distribution function $H(x): [0, \infty] \to [0, 1]$ by its

@@

    That is, $(x + K) \ln(1 + x/K)$ defined on $[0, \infty]$ is a convex

@@

    This expression can be simplified to
      \left(
        e^r + {\hat\phi \over 1 - \hat\phi}
      \right)^{-\xi} &>&
        \alpha e^{1/\alpha} \left[
          (K + q)^{-\alpha - 1} b + K^{-\alpha - 1}
        (\alpha + 1) e^{r \xi} \left[
          (K + q)^{-\alpha} b + K^{-\alpha}
      } \nonumber \\
      e^r + {\hat\phi \over 1 - \hat\phi} &<&
          (K + q)^{\alpha + 1} K + b K^{\alpha + 1} (K + q)
          b K^{\alpha + 1} + (K + q)^{\alpha + 1}
        } {
          \alpha
          \alpha + 1
      \right]^{-1/\xi}
      \exp \left(
        r - {1 \over \alpha \xi}
      \right) \nonumber \\
        {\alpha + 1 \over \alpha}
            b K^{\alpha + 1} + (K + q)^{\alpha + 1}
            b K^{\alpha+1} \left(1 + {q \over K} \right) + (K + q)^{\alpha + 1}
          \exp \left(
            r \xi - {1 \over \alpha}
          \right) \over K
      \right\}^{1/\xi} \nonumber \\
      \hat\phi &<& {e^r - g \over e^r - g - 1}

@@

@@

        {\alpha + 1 \over \alpha}

@@

            b K^{\alpha + 1} + (K + q)^{\alpha + 1}

@@

@@

            b K^{\alpha+1} \left(1 + {q \over K} \right) + (K + q)^{\alpha + 1}

@@

          \exp \left(
            r \xi - {1 \over \alpha}
          \right) \over K

@@

    Assumption \eqref{eq:xxie1.1} ensures $g < e^r - 1$. Hence the

@@

  \item When $q < 0$, we have
    \begin{eqnarray*}
      && \mathcal U(F)(\alpha, \beta, K, K', \hat\phi) \\
      &=& \alpha p K^\alpha (1 + b) \int_{-\infty}^0
      [(1 - \hat\phi) e^r + \hat\phi e^x]^{-\xi}
      (K - x)^{-\alpha-1} dx \\
      &&
      + (1 - p) \beta K'^\beta \left[
        (1 + b) \int_0^{-q} + \int_{-q}^\infty
      \right]
      [(1 - \hat\phi) e^r + \hat\phi e^x]^{-\xi} (K' + x)^{-\beta-1} dx    
    \end{eqnarray*}
  \end{enumerate}
  So the same calculation as in the previous case carries through
  with $q = 0$. The same conclusion of
  \[
  \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) > 0
  \]
  stands.
\end{proof}
\begin{remark}
  When $q = 0$, the lower-bound \eqref{eq:xxie1.1} on the interest
  rate simplifies to
  \begin{equation}
    \label{eq:xxie8}
    K < {
      (\alpha + 1) e^{-1/\alpha}
      \over
      \alpha (1 - e^{-r})^\xi
    }
  \end{equation}
  The right-hand-side of \eqref{eq:xxie8} is a very high upper bound
  on the scale parameter $K$, as is revealed later in this paper.
\end{remark}
